---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/UW-GAC/dbR.svg?branch=develop)](https://travis-ci.org/UW-GAC/dbR)

### dbR

Here are some utility functions for working with the in-house databases at the University of Washington Genetic Analysis Center (UW GAC).

### Installation

```{r installation, eval = FALSE}
devtools::install_github("UW-GAC/dbR")
```

### Quick demo

Get list of mySQL databases described in a ~/.mysql.cnf file via `list_from_cnf()`:

```{r, eval = FALSE}
library(dbR)
databases <- list_from_cnf('~/.mysql.cnf')
```

Get a mysql database connection to a database, `testdb`, which is listed in your .mysql.cnf file:

```{r, eval = FALSE}
con <- get_db_mysql("testdb")
```

or in a different .cnf file:

```{r, eval = FALSE}
con <- get_db_mysql("testdb", config = "~/.custom.cnf")
```

Get a dplyr sql src object connection to `testdb`:

```{r, eval = FALSE}
con <- dplyr_connect("testdb")
```

or to a different .cnf file:

```{r, eval = FALSE}
con <- dplyr_connect("testdb", config = "~/.custom.cnf")
```


